---
title: "Dashboard example: WHO"
author: "Anshu Uppal"
format: 
        dashboard:
                orientation: columns
                nav-buttons: [github]
                github: https://github.com/anshu-uppal/Dashboard_WHO
server: shiny

---

```{r}
#| context: setup
#| message: false

# Load packages
pacman::p_load(
  shiny,
  shinyWidgets,
  quarto,
  here,
  tidyverse,
  flextable,
  DT,
  plotly,
  leaflet,
  sf,
  htmltools
)
source(here::here("code", "utils.R"))

# Load data
rep_comb <- readRDS(here::here("data", "combined_dataset.rds"))
dataset_settings <- rep_comb |> group_by(dataset_id_name) |> count(setting) |> 
  mutate(setting_available = TRUE) |> 
  select(-n)

# Map data
settings_map_data <- readRDS(here::here("data", "world_settings_matched.rds"))

```

#  {.sidebar width="400px"}
```{r}
# Create the dropdown selection objects

# Select the Dataset
selectInput("selected_dataset", "Select Dataset:", 
            choices = unique(rep_comb$dataset_id_name), 
            selected = "Childhood immunization")

# Select the Indicator
selectInput("selected_indicator", "Select Indicator:", 
            choices = unique(rep_comb$indicator_name))

# Select the Dimension
selectInput("selected_dimension", "Select Dimension:", 
            choices = unique(rep_comb$dimension))

# Select the Region
selectInput("selected_region", "Select Region:", 
            choices = c("All", unique(rep_comb$whoreg6)), 
            selected = "European")

# Select the Setting
selectInput("selected_setting", "Select Setting(s):", 
            choices = unique(rep_comb$setting),
            multiple = TRUE
            # , options = pickerOptions(
            #         actionsBox = TRUE,
            #         selectOnTab = TRUE
            # )
)
```

```{r}
#| context: server
# Reactive expression to filter data to chosen Region
filtered_dataset <- reactive({
  rep_comb |> 
    filter(dataset_id_name == input$selected_dataset) |> 
    droplevels()
})

# Reactive expression to filter data to chosen Indicator
filtered_indicator <- reactive({
  filtered_dataset() |> 
    filter(indicator_name == input$selected_indicator) |> 
    droplevels()
})

# Reactive expression to filter data to chosen Region
filtered_region <- reactive({
  if(input$selected_region == "All") {
    filtered_dataset()
  } else{
    filtered_dataset() |> 
      filter(whoreg6 == input$selected_region) |> 
      droplevels()
  }
})

# Observe changes in the 'selected_region' input, and update setting choices
observeEvent(input$selected_region, {
  # Update the choices in the 'selected_indicateur' input
  updateSelectInput(
    session, "selected_setting",
    choices = sort(unique(filtered_region()$setting))
  )
})

filtered_setting <- reactive({
  if(length(input$selected_setting) == 0 || is.null(input$selected_setting)) {
    filtered_region()
  } else{
    filtered_region() |>
      filter(setting %in% c(input$selected_setting)) |>
      mutate(setting = fct_relevel(setting, c(input$selected_setting))) |>
      droplevels()
  }
})

# filtered_map_settings <- reactive({
#   tibble(setting = unique(filtered_setting()$setting)) |>
#     mutate(selected = "blue") |>
#     right_join(
#       settings_map_data |> # join with dataset to get countries available
#         left_join(dataset_settings |> 
#                                 filter(dataset_id_name == input$selected_dataset)
#                   )
#     ) |>
#     mutate(selected = case_when(
#       is.na(setting) ~ "grey70",
#       !setting_available ~ "grey70",
#       is.na(selected) ~ "lightgreen",
#       .default = selected)
#     ) |>
#     st_as_sf()
# })

# Observe changes in the 'selected_dataset' input, and update indicator choices
observeEvent(input$selected_dataset, {
  # Update the choices in the 'selected_indicator' input
  updateSelectInput(
    session, "selected_indicator",
    choices = sort(unique(filtered_dataset()$indicator_name))
  )
})

# Observe changes in the 'selected_indicator' input, and update dimension choices
observeEvent(input$selected_indicator, {
  # Update the choices in the 'selected_indicator' input
  updateSelectInput(
    session, "selected_dimension",
    choices = sort(unique(filtered_indicator()$dimension))
  )
})

```

## Map (in progress)
```{r}
leafletOutput("country_map")
```

```{r}
#| context: server
# output$plot <- renderPlot({
#         make_lineplot(
#                 dataset = filtered_setting(), 
#                 # whoreg6_choice = input$selected_region,
#                 indicator_name_choice = input$selected_indicator, 
#                 dimension_choice = input$selected_dimension
#         )
# })

output$plotly_plot <- renderPlotly({ 
  p <- make_lineplot(
    dataset = filtered_setting(), 
    # whoreg6_choice = input$selected_region,
    indicator_name_choice = input$selected_indicator, 
    dimension_choice = input$selected_dimension
  )
  
  ggplotly(
    p,
    tooltip = c("full_estimate", "year", "subgroup")
  ) 
}) 

# Layer of all countries
output$country_map <- renderLeaflet({
  leaflet() |>
    addTiles() |>
    addPolygons(
                data = settings_map_data,
                fillColor = "grey50",
                color = "black",  # Outline color
                weight = 1,
                label = ~htmltools::htmlEscape(admin)
    )
})

# Layer of countries available in dataset
observeEvent(input$selected_dataset, {
  leafletProxy("country_map", session) |> 
    clearGroup("available_countries") |> 
    addPolygons(
                data = settings_map_data |> filter(
                        setting %in% unique(filtered_dataset()$setting)),
                group = "available_countries",
                fillColor = "lightgreen",
                color = "black",  # Outline color
                weight = 1,
                label = ~htmltools::htmlEscape(admin)
        )
})

# Layer of countries available in selected region
observeEvent({
  input$selected_dataset 
  input$selected_region
  # input$selected_setting
  }, {
  leafletProxy("country_map", session) |> 
    clearGroup("selected_countries") |> 
    addPolygons(
                data = settings_map_data |> filter(
                        setting %in% unique(filtered_setting()$setting)),
                group = "selected_countries",
                fillColor = "blue",
                color = "black",  # Outline color
                weight = 1,
                label = ~htmltools::htmlEscape(admin)
        )
})

# Create the ESS-like table (still issues rendering this)
output$table <- renderUI(
  htmltools_value(
    make_table(
      dataset = filtered_setting(),
      caption_indicator = input$selected_indicator, 
      caption_dimension = input$selected_dimension
    )
  )
)

```

<!-- # Plot -->
<!-- ```{r} -->
<!-- plotOutput("plot") -->
<!-- ``` -->

# Setting plots
```{r}
plotlyOutput(outputId = "plotly_plot")
```

# Information
::: callout-note
This dashboard uses data from the WHO's ["Health Inequality Data Repository"](https://www.who.int/data/inequality-monitor/data):  

-  [Childhood immunization (DHS/MICS/RHS re-analyzed by ICEH)](https://www.who.int/data/sets/health-inequality-monitor-dataset#immunization) (updated October 2024)  
-  [Tuberculosis indicators](https://www.who.int/data/sets/health-inequality-monitor-dataset#tb) (updated June 2024)  
-  [HIV epidemiological estimates (UNAIDS)](https://www.who.int/data/sets/health-inequality-monitor-dataset#unaids-hiv) (updated October 2024)  

Next steps:  

-  Include option to add confidence intervals to plots  
-  Add page to view and download filtered data
-  Add mapping component to guide country selection?  
-  Added a basic map showing the available and selected settings  
-  Fun to tinker with this, but it does slow down the rendering.  
-  Temporarily deactivated while working on speeding it up.
:::
<!-- # Table -->
<!-- ```{r} -->
<!-- uiOutput("table") -->
<!-- ``` -->

